\documentclass[fleqn]{article}
\usepackage[utf8]{inputenc}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{relsize}

\title{\textbf{MATH 307: Individual Homework 22}}
\author{John Mays}
\date{05/02/21, Dr. Guo}

\begin{document}

\maketitle

\section*{Problem 1}
\subsubsection*{$A$ is invertible $\implies$ All of its singular values are nonzero.}
% $A$ is invertible $\implies$ $\det(A) \neq 0$.
Assume $A$ is not invertible $\implies \det(A) = 0$, and that it also has all nonzero singular values.\\
$$\det(A)=\det(U\Sigma V^{T})= \det(U)\det(\Sigma )\det(V^{T})=0$$
Both $U$ and $V$ are orthogonal matrices, therefore their determinants are nonzero.  Therefore, $\det(\Sigma) = 0$.\\
And since $\Sigma$ is a diagonal matrix, its determinant is the product of its diagonal entries.  Therefore $\det(0) \implies $ at least one $\sigma_i = 0 \rightarrow$ contradiction.\\
\linebreak
Therefore if $A$ is invertible, all of its singular values must be nonzero.
\subsubsection*{All of $A$'s singular values are nonzero $\implies$ it is invertible.}
If $A$ is invertible, then $A^{-1} = (U\Sigma V^{T}) = V \Sigma^{-1} U^{-1}$.\\
Note: $\Sigma$ is a diagonal matrix with the singular values along the diagonal.  In order to take the inverse of $\Sigma$, it is simply the reciprocal of all of the diagonal entries.\\
\linebreak
Assume one of the singular values is zero $\implies$ one of $\Sigma$'s diagonal entries is zero.  Taking the inverse would require taking the reciprocal of zero, therefore the singular value decomposition would not exist $\rightarrow$ contradiction: every matrix has a singular value decomposition.\\
\linebreak
Therefore all of $A$'s singular values must be nonzero in order for it to be\\ invertible.
\subsubsection*{Conclusion:}
Therefore $A$ is invertible $\iff$ All of its singular values are nonzero.
\pagebreak
\section*{Problem 2}
From properties of eigendecomposition, we know that if $A = Q \Lambda Q^{-1}$, then $-A = Q (-\Lambda)Q^{-1}$.  This implies that $-A$ will have the same eigenvalues as $A$, just negated.\\
\linebreak
\textbf{Characteristic Polynomial:}\\
\linebreak
$\det(\lambda I - (-A)) = (\lambda - (-\lambda_1))(\lambda - (-\lambda_2))\dots(\lambda - (-\lambda_n))$\\
Say $\lambda = 0$.  Then: \\
$\det(A) = (\lambda_1)(\lambda_2)\dots(\lambda_n)$\\
Therefore the determinant of A is the product of its eigenvalues.
\section*{Problem 3}
\subsubsection*{W.T.S. $A$ is invertible $ \implies \det(A) \neq 0$.}
If $A$ is invertible, $AA^{-1}=A^{-1}A=I$.\\
If $A$ is invertible, all of its eigenvalues must be nonzero, because $A^{-1}v=\frac{1}{\lambda}v$. \\
%$Assume A is $
$\det(AA^{-1})=\det(A^{-1}A)=\det(A^{-1})\det(A)=\det(I)=1$\\
Note that $A^{-1}$ is also invertible by definition, therefore its eigenvalues must also be nonzero.\\
Continuing, it is possible to write the determinant of $A$ in terms of $\det(A^{-1})$ as such:
$$\det(A)=\frac{1}{\det(A^{-1})}=\frac{1}{\lambda^{-1}_1\lambda^{-1}_2\dots \lambda^{-1}_n} \neq 0$$
\linebreak
Therefore if $A$ is invertible, its determinant must be nonzero.
\subsubsection*{W.T.S. $\det(A) \neq 0 \implies A$ is invertible.}
From \textbf{Problem 1}, if $A$ is not invertible, $A = U\Sigma V^{T}$, will have zero-values singular values (which are just $\sigma_i = \sqrt{|\lambda_i|}$.\\
$\det(A)= 0 = \det(U\Sigma V^{T})=\det(U)\det{\Sigma}\det(V^{T})=(\text(nonzero))\det(\Sigma)(\text(nonzero))\implies \det(\Sigma) = \sigma_1\sigma_2\dots\sigma_n \implies \lambda_1\lambda_2\dots\lambda_n = 0$\\
Therefore if $A$ is not invertible, it must have a zero-valued eigenvalue.\\
\linebreak
Contrapositively, if $\det(A) \neq 0,$ $A$ is invertible.
\subsubsection*{Conclusion: }
$\det(A) \neq 0 \iff A$ is invertible.

%Assume $\det(A) = 0$ and $A$ is also invertible.\\
%$\det(A)=\lambda_1\lambda_2\dots\lambda_n = 0 \implies \lambda_i = 0$ for some $1\leq i \leq n$. $\rightarrow$ contradiction: an invertible matrix must have eigenvalues





\end{document}